Cost- and Deadline-Constrained Provisioning for Scientific Workflow Ensembles in IaaS Clouds

### 2012-05-03 paper/paper.tex
makespan clarification

There are many applications that require scientific workflow ensembles.
CyberShake~\cite{Callaghan2011}, for example, uses ensembles to generate
seismic hazard maps.  Each workflow in a CyberShake ensemble generates a
hazard curve for a particular geographic location, and several hazard curves
are combined to create a hazard map.  In 2009 CyberShake was used to generate
a map that required an ensemble of 239 workflows.  Similarly, users of
Montage~\cite{Deelman2008} often need several workflows  with different
parameters to generate a set of image mosaics that can be combined  into a
single, large mosaic. The Galactic Plane ensemble, which generates several
mosaics of the  entire sky in different wavelengths, consists of 17 workflows,
each of which contains 900 sub-workflows.  Another ensemble example is the
Periodograms application~\cite{Vockler2011}, which searches for extrasolar
planets by detecting periodic dips in the light intensity of their host start.
Due to the large scale of the input data, this application is often split up
into multiple batches processed by different workflows. Additional workflows
are created to run the analysis using different parameters. A recent analysis
of Kepler satellite data required three ensembles of 15 workflows.

@@

Fig.~\ref{fig:variances} shows the results for estimate errors
ranging from $0\%$ to $50\%$. The figure summarizes the outcome of an
extensive suite of 525,000 simulations (10 ensembles of 50 workflows x 5
applications x 5 distributions x 10 budgets x 10 deadlines x 7 error values x
3 algorithms). The figure shows box plots of the ratio of the ensemble cost to
budget, and of ensemble makespan to deadline. The ratio indicates whether the value 
(for example, the simulated cost) exeeded the constraint (the budget). Values
greater than 1 indicate that the constraint was exceeded.

@@

Fig.~\ref{fig:variances}.b shows the ratio of simulated makespan to budget. 
Interestingly, the deadline constraint is rarely exceeded, even in cases with
very poor quality estimates. For the dynamic algorithms this is a result of
the fact that they can adapt to poor estimates. For the static algorithm this
is a result of the way that SPSS schedules workflows, and not of a
particularly clever optimization. The SPSS algorithm tends to schedule
workflows early, using up the budget long before the deadline is reached. This
is a consequence of the deadline distribution function in SPSS, which prevents
workflows from starting late. This is illustrated by the gantt chart in
Fig.~\ref{fig:algorithm-example}.b, which shows how SPSS tends to pile
up workflows at the beginning of the timeline. 
%In comparison, the dynamic
%algorithms tend to spread out workflow starts over the entire duration as
%shown in Fig.~\ref{fig:algorithm-example}.a. The consequence of this
%behavior is that SPSS plans tend to use up the budget but leave plenty of time
%before the deadline. 
As a result, when the runtime of the plan is increased by
introducing errors, the SPSS plan has some room to expand without exceeding
the deadline.

>>>>

There are many applications that require scientific workflow ensembles.
CyberShake~\cite{Callaghan2011}, for example, uses ensembles to generate
seismic hazard maps.  Each workflow in a CyberShake ensemble generates a
hazard curve for a particular geographic location, and several hazard curves
are combined to create a hazard map.  In 2009 CyberShake was used to generate
a map that required an ensemble of 239 workflows.  Similarly, users of
Montage~\cite{Deelman2008} often need several workflows  with different
parameters to generate a set of image mosaics that can be combined  into a
single, large mosaic. The Galactic Plane ensemble, which generates several
mosaics of the  entire sky in different wavelengths, consists of 17 workflows,
each of which contains 900 sub-workflows.  Another ensemble example is the
Periodograms application~\cite{Vockler2011}, which searches for extrasolar
planets by detecting periodic dips in the light intensity of their host star.
Due to the large scale of the input data, this application is often split up
into multiple batches processed by different workflows. Additional workflows
are created to run the analysis using different parameters. A recent analysis
of Kepler satellite data required three ensembles of 15 workflows.

@@

Fig.~\ref{fig:variances} shows the results for estimate errors
ranging from $0\%$ to $50\%$. The figure summarizes the outcome of an
extensive suite of 525,000 simulations (10 ensembles of 50 workflows x 5
applications x 5 distributions x 10 budgets x 10 deadlines x 7 error values x
3 algorithms). The figure shows box plots of the ratio of the ensemble cost to
budget, and of ensemble makespan to deadline. Whiskers on the plots
indicate maximum and minimum values. The ratio indicates whether the value 
(for example, the simulated cost) exeeded the constraint (the budget). Values
greater than 1 indicate that the constraint was exceeded.

@@

Fig.~\ref{fig:variances}.b shows the ratio of simulated makespan to budget.
Interestingly, the deadline constraint is rarely exceeded, even in cases with
very poor quality estimates. For the dynamic algorithms this is a result of the
fact that they can adapt to poor estimates and stop submitting new tasks when
the constraints are reached. Makespan is then computed as the finish time of the
last fully completed workflow from the ensemble. For the static algorithm this
is a result of the way that SPSS schedules workflows, and not of a particularly
clever optimization. The SPSS algorithm tends to schedule workflows early, using
up the budget long before the deadline is reached. This is a consequence of the
deadline distribution function in SPSS, which prevents workflows from starting
late. This is illustrated by the gantt chart in
Fig.~\ref{fig:algorithm-example}.b, which shows how SPSS tends to pile up
workflows at the beginning of the timeline.
% In comparison, the dynamic algorithms tend to spread out workflow starts over
% the entire duration as shown in Fig.~\ref{fig:algorithm-example}.a. The
% consequence of this behavior is that SPSS plans tend to use up the budget but
% leave plenty of time before the deadline.
As a result, when the runtime of the plan is increased by introducing errors,
the SPSS plan has some room to expand without exceeding the deadline.
